\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-20 body.tex
Adding pseudo-Agda into appendix. I actually have no better idea to include them but only attach a link. Please check.

\section{Metatheory in (pseudo-)Agda}
We make three agda source code files (publicly and anonymously) openly avaliable that include the corresponding QIIT syntax definition and models.

>>>>

\section{Metatheory in (pseudo-)Agda}
We make three agda source code files (publicly and anonymously) openly avaliable, and they include the corresponding QIIT syntax definition and models.
